Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-13 report.Rmd
add ratio_dm
add table

@@

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```
```{r}
sma_sp_tab |>
  write_csv("data/sma_sp_tab.csv")
```

@@

>>>>

## punch

```{r, eval=TRUE}
tar_load(sma_tab_large)
sma_tab_large |>
  kable() |>
  kable_styling()
```

```{r, eval=TRUE}
tar_load(sma_tab_small)
sma_tab_small |>
  kable() |>
  kable_styling()
```

@@

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```

```{r}
sma_sp_tab |>
  write_csv("data/sma_sp_tab.csv")
```

@@

# DM and HDK

```{r}
tar_load(tree)
fit <- lm(log(lma_leaf / lma_disc) ~ log(dry_mass_disc), tree)
lmtest::bptest(fit)
```
